\plaintitle

### 2016-12-31 drafts/labor/introduction.tex
piecework changes to intro and lit review

\topic{As on--demand work has grown far beyond information work, it has given rise to an increasingly complex, conflicted culture amongst both the workers who enable it and the researchers who study it.}
\citeauthor{howe2008crowdsourcing} first described crowdsourcing broadly as
``outsourcing to an undefined, generally large group of people in the form of an open call''~\cite{howe2008crowdsourcing}.
However, for years its instantiation was limited to the utilization of
human intelligence to process data, participate in scientific studies, and perform information work~\cite{CrowdsourcingUserStudies,movieSummarizationWu,
      yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.
More recently, crowdsourcing of physically embodied work
--- driving and cleaning, for instance ---
has become a focus for on--demand labor markets~\cite{uberAlgorithm,uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
This growth prompted efforts to understand not just the work, but also the workers on these platforms~\cite{Ross,whoareNOTtheTurkers}.
Some of this research has been motivated by the identification of the sociality of gig work,
and the frustration and disenfranchisement that these systems embody~\cite{turkopticon,martin2014being,takingAHITMcInnis}.
Other work has focused on the outcomes of this frustration,
reflecting on the resistance workers express against digitally mediated labor markets~\cite{uberAlgorithm,dynamo}.

\topic{This body of research has broadly sought to answer one central question:
What does the future hold for on--demand work and those who do it?}
Researchers have offered insights on this question along three major threads.
\begin{Numberlist}[itemjoin*={.~And~},itemjoin={.~}]
  \item \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}[label=(\alph*)]
          \item How complex are the goals that crowd work can accomplish?, and
          \item What kinds of goals and industries may eventually utilize it?
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364}
  \item \nameref{sec:decomposition}
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}
  \item \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}.
\end{Numberlist}

This research has largely sought to answer these questions by examining extant on--demand work phenomena.
So far, it has not offered a framing for holistically explaining
the developments in worker processes that researchers have developed, or
the emergent phenomena in social environments;
nor has any research
% , to our knowledge,
gone so far as to directly predict future developments.

\subsection{Piecework as a lens to understand crowdsourcing}
In this paper, we offer a framing for on--demand work as a contemporary instantiation of \textit{piecework}: %\namerefl{sec:pieceworkArc} ---
a work and payment structure which breaks tasks down into standalone contracts,
wherein payment is made for work output, rather than for time.
Piecework as a metaphor for crowd work is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeyear{crowdworkFuture}
referenced crowd work as piecework briefly
as a loose analogy to the form of work emerging at the time~\cite{crowdworkFuture}.
But more than this,
the framing of on--demand labor as a re--instantiation of piecework
gives us years of historical material to make sense of this new form of work, and allows us to reflect on--demand work through a mature theoretical lens, informed by decades of rigorous, empirically based research.

More concretely, by looking at on--demand work as
an instantiation (or even a continuation) of piecework,
and by looking for patterns that the corresponding literature predicts
on this basis, we can:
\begin{numberlist}[itemjoin*={;~and~},itemjoin={;~}]
  \item make sense of past events as part of a much larger series of an interrelated phenomenon
  \item reflect on differences in the factors that impacted piecework historically and impact on--demand work today
  \item to some extent, offer predictions of what on--demand work researchers,
        and workers themselves,
        might expect to see on the horizon.
\end{numberlist}
For example, we will draw on the piecework literature studying task decomposition,
which was historically limited by technological limits in measurement and instrumentation, and
leverage that understanding to suggest how modern technology affects this mechanism in on--demand work.

We organize this paper as follows: we first review the definition and historical arc of piecework to lay  groundwork and make clear the analogy to on--demand work (which we will refer to as \textit{crowd work} subsequently, for consistency with prior literature). Then, we interrogate the three major research questions above using the lens of piecework. 
We will identify similarities and differences between piecework as historically understood and
on--demand work as we experience it today.
Finally, we will make predictions of future developments based on how those similarities and differences influenced piecework.
Finally, we will offer implications for researchers and practitioners based on our results.

\onlyinsubfile{
  \balance{}
  \printbibliography
}

>>>>

\topic{As on--demand work has grown far beyond information work, it has given rise to an increasingly complex, conflicted culture amongst both the workers who enable it and the researchers who study it.}
\citeauthor{howe2008crowdsourcing} first described crowdsourcing broadly as
``outsourcing to an undefined, generally large group of people in the form of an open call''~\cite{howe2008crowdsourcing}.
However, for years its instantiation was limited to the utilization of
human intelligence to process data, participate in scientific studies, and perform information work~\cite{CrowdsourcingUserStudies,movieSummarizationWu,yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.
More recently, crowdsourcing of physically embodied work
--- driving and cleaning, for instance ---
has become a focus for on--demand labor markets~\cite{uberAlgorithm,uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
This growth prompted efforts to understand not just the work, but also the workers on these platforms~\cite{Ross,whoareNOTtheTurkers}.
Some of this research has been motivated by the identification of the sociality of gig work~\cite{crowdcollab},
and the frustration and disenfranchisement that these systems embody~\cite{turkopticon,martin2014being,takingAHITMcInnis}.
Other work has focused on the outcomes of this frustration,
reflecting on the resistance workers express against digitally mediated labor markets~\cite{uberAlgorithm,dynamo}.

\topic{This body of research has broadly sought to answer one central question:
What does the future hold for on--demand work and those who do it?}
Researchers have offered insights on this question along three major threads:
\begin{numberlist}[itemjoin*={;~and~},itemjoin={;~}]
  \item \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}[label=(\alph*)]
          \item How complex are the goals that crowd work can accomplish?, and
          \item What kinds of goals and industries may eventually utilize it?
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364}
  \item \nameref{sec:decomposition}
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}
  \item \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}.
\end{numberlist}

This research has largely sought to answer these questions by examining extant on--demand work phenomena.
So far, it has not offered a framing for holistically explaining
the developments in worker processes that researchers have developed, or
the emergent phenomena in social environments;
nor has any research
gone so far as to directly predict future developments.

\subsection{Piecework as a lens to understand crowdsourcing}
In this paper, we offer a framing for on--demand work as a contemporary instantiation of \textit{piecework},
a work and payment structure which breaks tasks down into standalone contracts,
wherein payment is made for work output, rather than for time.
Piecework as a metaphor for crowd work is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeyear{crowdworkFuture}
referenced crowd work as piecework briefly
as a loose analogy to the form of work emerging at the time~\cite{crowdworkFuture}.
But more than this,
the framing of on--demand labor as a re--instantiation of piecework
gives us years of historical material to make sense of this new form of work, and allows us to reflect on--demand work through a mature theoretical lens, informed by decades of rigorous, empirically based research.

More concretely, by looking at on--demand work as
an instantiation (or even a continuation) of piecework,
and by interrogating patterns that the corresponding literature predicts
on this basis, we can
\begin{numberlist}[itemjoin*={; and },itemjoin={;~}]
  \item make sense of past events as part of a much larger series of an interrelated phenomenon
  \item reflect on differences in the factors that impacted piecework historically and their impact on--demand work today
  \item to some extent, offer predictions of what on--demand work researchers,
        and workers themselves,
        might expect to see on the horizon.
\end{numberlist}
For example, we will draw on the piecework literature regarding task decomposition,
which was historically limited by shortcomings in measurement and instrumentation, and
leverage that understanding to suggest how modern technology affects this mechanism in on--demand work.

We organize this paper as follows:
\begin{numberlist}[itemjoin*={; and },itemjoin={;~}]
  \item we review the definition and historical arc of piecework
  to lay groundwork and make clear the analogy to on--demand work
  (which we'll call \textit{crowd work} hereon
  for consistency with the existing literature)
  \item we interrogate the three major research questions above using the lens of piecework. 
  We will identify similarities and differences between piecework as historically understood and
  on--demand work as we know it today
  \item we will make predictions of future developments based on how those similarities and differences influenced piecework
  \item we will offer implications for researchers and practitioners based on our results.
\end{numberlist}

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
% }

### 2016-12-31 drafts/labor/piecework_lit.tex
piecework changes to intro and lit review

\onlyinsubfile{\clearpage}
\section{A Review of Piecework}

\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor,
but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally),
this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the the rest of the argument.
Specifically, we will
\begin{inlinelist}[itemjoin*={;~and~},itemjoin={;~}]
  \item define ``piecework'' as researchers in the topic understood it
  \item trace the rise and fall of piecework at a very high level,
        identifying key figures and ideas during this time
\end{inlinelist}
This section is not intended to be comprehensive: instead, it sets up the scaffolding necessary for our later investigations of crowd work's three questions: complexity limits, task decomposition, and worker relationships.

% \onlyinsubfile{\clearpage}
\subsection{What is piecework?}
\topic{Aligning on--demand work with piecework requires an understanding of what piecework is.}
While ``piecework'' has had multiple definitions over time,
we can trace a constellation of characteristics that recur throughout the literature.
We will follow this history of research, collecting
descriptions,
examples, and
provided definitions of piecework, trying
to trace the outline of a working understanding of
\textit{what piecework is}.

\citeauthor{hughRaynbirdTaskWork} offers
a concise definition of piecework
--- which he variously also calls ``measure work'', ``grate work'', and ``task work'' ---
by contrasting the ``task--labourer'' with the ``day--labourer'':
``the chief difference lies between the day--labourer,
who receives a certain some of money\dots~for his day's work,
and the task--labourer, whose earnings depend on the \textit{quantity} of work done [emphasis added]''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} gives a more illustrative definition of piecework,
offering examples:
``payment is made for each hectare which is pronounced to be well ploughed~[\dots]~
for each living foal got from a mare;~[\dots]~
for each living calf got''~\cite{10.2307/2338394}.
This framing perhaps makes the most intuitive sense;
``payment for results,'' as \citeauthor{10.2307/2338394} calls it,
is not only common in practice, but well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

\topic{It's worth acknowledging that
``this distinction [between piece--rates and time--rates] was not completely clear--cut''~\cite{hart2013rise}.}
Indeed, work adopted piece--rate compensation in some aspects and
time--rate compensation in others.
The ``Rowan premium system'',
which essentially paid workers
a base rate for time plus
(the potential for) an additional pay dependent on output,
was just one of several alternatives to stricter time-- and piece--rate renumeration paradigms, which
muddies the waters for us later as we attempt to categorize cases of piecework~\cite{rowan1901premium}.
As \citeauthor{rowan1901premium}'s premium system guaranteed an hourly rate
regardless of the worker's productive output
\textit{as well as} an additional compensation tied to performance,
workers under this regime were
in some senses ``task--labourers'', and
in other senses (more conventional) ``day--labourers''.

\topic{It may be worth thinking about piecework through the lens of its \textit{emergent} properties to help understand it.}
Returning to
\citeauthor{hughRaynbirdTaskWork}, several arguments for the merits of piecework
crop up; he points out that 
``piece work holds out to the labourer an increase of wages as a reward for his skill and exertion~[\dots]~
he knows that all depends on his own diligence and perseverance~[\dots and]~
so long as he performs his work to the satisfaction of his master,
he is not under that control to which the day--labourer is always subject.''
\citeauthor{hughRaynbirdTaskWork} highlight the freedom from control that ``task--labourers'' enjoy~\cite{hughRaynbirdTaskWork,rowan1901premium}.

\topic{We see this sense of independence regardless of the time, locale, and industry.}
\citeauthor{10.2307/3827491} offers a look into the lives and culture of ``match--girls''
--- young women paid by piecework to assemble matchsticks generally in the late \nth{19} century.
Of particular interest was their independent nature, via their reputation ``\dots~for generosity, independence, and protectiveness,
but also for brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
\citeauthor{10.2307/27508091} documents piecework from 1850--1930 in Australia,
finding similar assertions of the freedom compositors of newspapers experienced as pieceworkers:
``If a piece--work compositor who held a `frame' decided that he did not want to work on a particular day or night,
the management recognised his right to put a `substitute' or `grass' compositor in his place''~\cite{10.2307/27508091}.
From these accounts we identify a sense of independence and autonomy that resonates across decades, industries, and locales where piecework is found.

\topic{Piecework opened the door for people who previously couldn't participate in the labor market --- for example due to lack of training --- to do so, and to acquire job skills incrementally.}
For example, women could receive training in narrow subsets of the general body of skills, enabling them to act in capacities similar to what conventional (male) apprentices would undertake~\cite{hart2013rise}.
In addition, workers with specific slices of skills could be matched to suitable tasks.
Workers without conventional training
--- like women, who had no such opportunities
to engage in engineering and metalworking apprenticeships as men did ---
could be trained very narrowly on a very tightly constrained task,
demonstrate proficiency, and become experts in their own ways.

@@

% \ali{I'm looking into \citeauthor{grier2013computers}'s book to see if there's more about the relationships workers had with Airy.
% Maybe I can/should expand this to discuss other implementations of human computation around this time (if I find any good anecdotes).}
\onlyinsubfile{\clearpage}
\subsubsection{Railroad and other Industrial Workers}
{Piecework might be most familiar to the HCI researcher in the context of the assembly line, which largely defined manufacturing through the \nth{20} century.}
It was here that
scientific management, Fordism, and Taylorism
dramatically influenced how workers were managed and
the ways in which workers were perceived and envisioned paradigmatically;
it's here we'll start our overview of piecework's history through case studies.

@@

\onlyinsubfile{\clearpage}
\subsubsection{Domestic and Farmhand Labor}
\topic{When piecework entered the American economy, it was not used for complex work.}
One reason for low complexity was workers' skills:
it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted~\cite{hart2013rise}.
So, initially piecework in the United States arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
The complexity of the work remained low at the turn of
the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage~\cite{burton1899commercial} and
management regimes~\cite{norton1900textile}
rather than training.
Mass manufacturing,
such as sewing garments~\cite{riisOtherSideLives} and making matchsticks~\cite{10.2307/3827491},
flourished under piecework systems in densely populated cities.

@@

\onlyinsubfile{\clearpage}
\subsubsection{Airy's Computers}
\topic{Some of the first systematic cases of what we would recognize as crowd work
can be found in the study of astronomy.}
In the \nth{19} century, the calculation of celestial bodies had become
a competitive field with 
Airy needed to compute tables that would
allow sailors to locate themselves by starlight from sea.
This work ostensibly called for educated people who comprehensively understood mathematics.
Airy realized that he could break the tasks down and delegate the constituent parts
to ``human computers'' who
``\dots~possessed the basic skills of mathematics,
including `Arithmetic, the use of Logarithms, and Elementary Algebra'~''~\cite{grier2013computers}.
As a result, many of Airy's computers had relatively rudimentary educations
compared to the background of education that typically worked in the calculation of solar tables.
Airy distributed tasks by mail,
allowing work to be completed by a somewhat geographically distributed workforce,
and paid for each piece of work completed.
% \ali{also talk about the challenge/competition Airy was in with other astronomers,
% and the approach of verifying worker results}
% Airy's method of distributing work was unorthodox, but his workforce management style was especially unconventional.
% For one thing,
Airy also instituted a policy of firing his computers once they reached age 23.

@@

\onlyinsubfile{
  % \printbibliography
  }

>>>>

% \onlyinsubfile{\clearpage}
\section{A Review of Piecework}

\topic{The HCI community has used the term ``piecework'' to describe
myriad instantiations of on--demand labor,
but this reference has generally been offered in passing.}
As this paper principally traces a relationship between
the historical piecework and the contemporary crowd work
(or on--demand labor more generally),
this casual familiarity with piecework may prove insufficient.
We'll more carefully discuss piecework in this section in order
to inform the the rest of the argument.
Specifically, we will
\begin{numberlist}[itemjoin*={, and },label={\nthwords*}]
  \item define ``piecework'' as researchers in its field understand it
  \item trace the rise and fall of piecework at a high level,
        identifying key figures and ideas during this time.
\end{numberlist}
This section is not intended to be comprehensive: instead, it sets up the scaffolding necessary for our later investigations of crowd work's three questions: complexity limits, task decomposition, and worker relationships.

% \onlyinsubfile{\clearpage}
\subsection{What is piecework?}
\topic{Aligning on--demand work with piecework requires an understanding of what piecework is.}
While it has had several definitions over time,
we can trace a constellation of characteristics that recur throughout the literature.
We'll follow this research, collecting
descriptions,
examples, and
definitions of piecework,
tracing an outline of % a working understanding of
\textit{what piecework is}.

\citeauthor{hughRaynbirdTaskWork} provides
a concise definition of piecework
(which he also calls ``measure work'', ``grate work'', and ``task work'')
by contrasting with the ``day--labourer'':
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} defines it through examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing offers a more intuitive sense;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

\topic{It's worth acknowledging that
``this distinction [between piece--rates and time--rates] was not completely clear--cut''~\cite{hart2013rise}.}
Indeed, employers adopted piece--rate compensation in some aspects and
time--rate compensation in others.
The Rowan premium system,
which essentially paid workers
a base rate for time plus, potentially,
an additional pay dependent on output~\cite{rowan1901premium};
this was just one of several alternatives to categorical time-- and piece--rate renumeration paradigms.
% which will complicate our categorization of cases of piecework.
As \citeauthor{rowan1901premium}'s premium system guaranteed an hourly rate
regardless of the worker's productive output
\textit{as well as} additional compensation tied to performance,
workers under this regime were
in some senses ``task--labourers'', but
in other senses ``day--labourers''.

\topic{It may be worth thinking about piecework through the lens of its \textit{emergent} properties to help understand it.}
\citeauthor{hughRaynbirdTaskWork} argues for the merits of piecework, % do you like what i did there?
pointing out that
``piece work holds out to the labourer an increase of wages as a reward for his skill and exertion~\dots~he knows that all depends on his own diligence and perseverance~\dots~[and] so long as he performs his work to the satisfaction of his master, he is not under that control to which the day--labourer is always subject''.
The argument that ``task--labourers'' enjoy freedom from control crops up in \citeauthor{hughRaynbirdTaskWork}'s and later \citeauthor{rowan1901premium}'s works~\cite{hughRaynbirdTaskWork,rowan1901premium}.

\topic{We see this sense of independence in myriad times, locales, and industries.}
\citeauthor{10.2307/3827491} offers a look into the lives and culture of ``match--girls''
--- young pieceworkers, mostly women, who assembled matchsticks in the late \nth{19} century.
Of interest was their reputation ``\dots~for generosity, independence, and protectiveness,
but also for brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
\citeauthor{10.2307/27508091} document piecework from 1850 through 1930 in Australia,
finding similar assertions of the freedom compositors of newspapers experienced as pieceworkers:
``If a piece--work compositor~\dots~decided that he did not want to work on a particular day or night,
the management recognised his right to put a `substitute' or `grass' compositor in his place''~\cite{10.2307/27508091}.
We therefore draw a \textit{sense} of independence and autonomy inherent to piecework.
%that resonates across decades, industries, and locales where piecework is found.

\topic{Piecework opened the door for people who previously couldn't participate in the labor market to do so, and to acquire job skills incrementally.}
During World War II, women received training in narrow subsets of more comprehensive jobs, enabling work in capacities similar to conventional (i.e. male) workers~\cite{hart2013rise}.
Workers with specific skill subsets could be matched to suitable tasks.
Women previously had virtually no opportunities
to engage in engineering and metalworking apprenticeships as men did;
now, they
could be trained quickly on narrowly scoped tasks,
demonstrate proficiency, and become experts.

@@

% \ali{I'm looking into \citeauthor{grier2013computers}'s book to see if there's more about the relationships workers had with Airy.
% Maybe I can/should expand this to discuss other implementations of human computation around this time (if I find any good anecdotes).}
% \onlyinsubfile{\clearpage}
\subsubsection{Railroad and other Industrial Workers}
{Piecework might be most familiar to the HCI researcher in the context of the assembly line, which largely defined manufacturing through the \nth{20} century.}
It was here that
scientific management, Fordism, and Taylorism
dramatically influenced how workers were managed and
the ways in which workers were perceived and envisioned paradigmatically;
it's here we'll start our overview of piecework's history through case studies.

@@

% \onlyinsubfile{\clearpage}
\subsubsection{Domestic and Farmhand Labor}
\topic{When piecework entered the American economy, it was not used for complex work.}
One reason for low complexity was workers' skills:
it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted~\cite{hart2013rise}.
So, initially piecework in the United States arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
The complexity of the work remained low at the turn of
the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage~\cite{burton1899commercial} and
management regimes~\cite{norton1900textile}
rather than training.
Mass manufacturing,
such as sewing garments~\cite{riisOtherSideLives} and making matchsticks~\cite{10.2307/3827491},
flourished under piecework systems in densely populated cities.

@@

% \onlyinsubfile{\clearpage}
\subsubsection{Airy's Computers}
\topic{Some of the first systematic cases of what we would recognize as crowd work
can be found in the study of astronomy.}
In the \nth{19} century, the calculation of celestial bodies had become
a competitive field with 
Airy needed to compute tables that would
allow sailors to locate themselves by starlight from sea.
This work ostensibly called for educated people who comprehensively understood mathematics.
Airy realized that he could break the tasks down and delegate the constituent parts
to ``human computers'' who
``\dots~possessed the basic skills of mathematics,
including `Arithmetic, the use of Logarithms, and Elementary Algebra'~''~\cite{grier2013computers}.
As a result, many of Airy's computers had relatively rudimentary educations
compared to the background of education that typically worked in the calculation of solar tables.
Airy distributed tasks by mail,
allowing work to be completed by a somewhat geographically distributed workforce,
and paid for each piece of work completed.
% \ali{also talk about the challenge/competition Airy was in with other astronomers,
% and the approach of verifying worker results}
% Airy's method of distributing work was unorthodox, but his workforce management style was especially unconventional.
% For one thing,
Airy also instituted a policy of firing his computers once they reached age 23.

@@

\onlyinsubfile{
  \printbibliography
  }
